### 2015-11-30 README.Rmd
udpated cran comments and news, and fixed a test updated readme

	<td style="text-align:left;">Phylomatic</td>
	<td style="text-align:left;"><code>phylomatic</code></td>
	<td style="text-align:left;"><a href="http://phylodiversity.net/phylomatic/html/documentation.html">link</a></td>

@@

	<td style="text-align:left;">Global Invasive Species Database</td>
	<td style="text-align:left;"><code>gisd</code></td>
	<td style="text-align:left;">***</td>

@@

@@

#### May be in taxize in the future...

+ [NatureServe](http://www.natureserve.org/)
+ [Lichen Taxon dictionary](http://www.thebls.org.uk/)
+ [Wikispecies](https://species.wikimedia.org/wiki/Main_Page)
+ And more, See the [newdatasource](https://github.com/ropensci/taxize/labels/newdatasource) tag in the issue tracker

## Quickstart

@@

### Installation

#### Stable version from CRAN

@@

#### Development version from GitHub

@@

### Get unique taxonomic identifier from NCBI

@@

### Retrieve classifications

@@

### Immediate children

@@

### Downstream children to a rank

@@

### Upstream taxa

@@

### Get synonyms

@@

### Get taxonomic IDs from many sources

@@

### Common names from scientific names

@@

### Scientific names from common names

@@

### Coerce codes to taxonomic id classes

@@

### Coerce taxonomic id classes to a data.frame

>>>>

@@

@@

	<td style="text-align:left;">Index Fungorum</td>
	<td style="text-align:left;"><code>fg</code></td>
	<td style="text-align:left;"><a href="http://www.indexfungorum.org/ixfwebservice/fungus.asmx">link</a></td>
	<td style="text-align:left;">EU BON</td>
	<td style="text-align:left;"><code>eubon</code></td>
	<td style="text-align:left;"><a href="http://cybertaxonomy.eu/eubon-utis/doc.html">link</a></td>
	<td style="text-align:left;">Index of Names (ION)</td>
	<td style="text-align:left;"><code>ion</code></td>
	<td style="text-align:left;"><a href="http://www.organismnames.com/">link</a></td>

@@

### May be in taxize in the future...

See the [newdatasource](https://github.com/ropensci/taxize/labels/newdatasource) tag in the issue tracker

## Tutorial

@@

## Installation

### Stable version from CRAN

@@

### Development version from GitHub

@@

## Get unique taxonomic identifier from NCBI

@@

## Retrieve classifications

@@

## Immediate children

@@

## Downstream children to a rank

@@

## Upstream taxa

@@

## Get synonyms

@@

## Get taxonomic IDs from many sources

@@

## Common names from scientific names

@@

## Scientific names from common names

@@

## Coerce codes to taxonomic id classes

@@

## Coerce taxonomic id classes to a data.frame
